---
title: "API Summary Report"
output: html_document
params:
  mindate: 'NA'
  maxdate: 'NA'
  data_source: 'all'
  user: 'all'
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

library(auditR)
library(tidyverse)
library(lubridate)
library(DT)
library(hms)
library(echarts4r)
library(magrittr)
library(knitr)
library(formattable)
library(echarty)

df <- get_api_logs(env = 'prod')

df$attributes.transaction.start_datetime <- as_datetime(df$attributes.transaction.start_datetime)

df$attributes.transaction.end_datetime <- as_datetime(df$attributes.transaction.end_datetime)

df$time_to_transmit_in_secs <- difftime(df$attributes.transaction.end_datetime, df$attributes.transaction.start_datetime)
  

#Getting CDC vs non-CDC
#100 and 101 = CDC, all else = non-CDC
#Merge user id of get_userbase with df to get sites

sites <- get_userbase()

df <- merge(df, sites, by.x = "user_id", by.y = "Login", all.x = TRUE)

df$cdc <- ifelse(df$Site_ID == 100 | df$Site_ID == 101, "CDC", "Non-CDC")

df$cdc <- ifelse(df$user_id == "anonymous", "Unknown", df$cdc)

#Following parameters
if (params$mindate != 'NA'){
  df <- df %>% 
    filter(attributes.transaction.start_datetime >= params$mindate)
}

if (params$maxdate != 'NA'){
  df <- df %>% 
    filter(attributes.transaction.start_datetime <= params$maxdate)
}


 if (!("all" %in% params$data_source)) {
   df <- df %>% 
     filter(attributes.params$datasource %in% params$data_source)
 }

if (!("all" %in% params$user)) {
   df <- df %>% 
     filter(user_id %in% params$user)
 }


#Saving initial df as df_raw
df_raw <- df

#Turning usual df into successful requests only
df <- df %>% 
  filter(attributes.transaction.status_code >= 200 & attributes.transaction.status_code <= 299)


#Getting basic one-column tables for narrative
app_names <- df %>%
  group_by(attributes.params.datasource) %>% 
  summarise(raw_requests = n())

names(app_names) <- c("Data Source", "Raw Requests")

user_ids <- df %>% 
  group_by(user_id) %>% 
  summarise(raw_requests = n())

names(user_ids) <- c("User ID", "Raw Requests")
```


*Report generated `r format(Sys.time(), '%d %B %Y')`.*

*Log records range from `r min(as_datetime(na.omit(df$attributes.transaction.start_datetime)))` to `r max(as_datetime(na.omit(df$attributes.transaction.end_datetime)))`.*

This report contains user metrics for API requests from the following data sources and user IDs: 
`r DT::datatable(app_names, filter = "top", rownames = FALSE)`  
`r DT::datatable(user_ids, filter = "top", rownames = FALSE)` 


```{r table, results = 'asis', echo = FALSE}

summary_table <- df_raw %>% 
  group_by(attributes.params.datasource) %>% 
  summarise(median_time_to_transmit = median(time_to_transmit_in_secs),
            total_requests = n())

successful_table <- df_raw %>% 
  filter(attributes.transaction.status_code >= 200 & attributes.transaction.status_code <= 299) %>% 
  group_by(attributes.params.datasource) %>% 
  summarise(successful_requests = n())

summary_table <- merge(summary_table, successful_table, 
                       by = "attributes.params.datasource",
                       all = TRUE)

cdc_proportion <- as.data.frame(prop.table(table(df_raw$attributes.params.datasource, df_raw$cdc),1))

cdc_proportion <- subset(cdc_proportion, Var2 == "CDC", select = c(Var1, Freq))

names(cdc_proportion) <- c("datasource", "freq")

summary_table <- merge(summary_table, cdc_proportion, 
                       by.x = "attributes.params.datasource",
                       by.y = "datasource", all.x = TRUE)

summary_table$median_time_to_transmit <- as_hms(summary_table$median_time_to_transmit)

summary_table$freq <- round(summary_table$freq * 100, 2)

summary_table$freq <- ifelse(is.na(summary_table$freq), 0, summary_table$freq)

summary_table$successful_requests <- ifelse(is.na(summary_table$successful_requests), 0, summary_table$successful_requests)

summary_table$total_requests <- ifelse(is.na(summary_table$total_requests), 0, summary_table$total_requests)

names(summary_table) <- c("Data Source", "Median Time to Transmit", 
                          "Total Requests", "Successful Requests",
                          "Percent of Users CDC")
DT::datatable(summary_table,
              caption = "Summary Table of API Usage", 
              rownames = FALSE,
        selection = list(mode = "multiple",  
                         selected = rownames(design.df)[1:nrow(design.df)]))

```

```{r heatmap, results = 'asis', echo = FALSE}
df$day_of_week <- wday(
  df$attributes.transaction.start_datetime,
  label = TRUE,
  abbr = TRUE
)

df$hour_of_day <- hour(
  df$attributes.transaction.start_datetime
)

heatmap_df <- df %>% group_by(hour_of_day, day_of_week) %>% 
  summarise(logins = n()) %>% 
  dplyr::ungroup() %>% 
  arrange(hour_of_day, day_of_week)
# 
# wdays <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
# hours <- 1:24
# perms <- data.frame(expand.grid(hours, wdays))
# names(perms) <- c("hour_of_day", "day_of_week")
# 
# heatmap_df <- merge(heatmap_df, perms, all = TRUE)

#heatmap_df$logins <- ifelse(is.na(heatmap_df$logins), 0, heatmap_df$logins)

# df$hour_of_day <- as.character(df$hour_of_day)

heatmap_df <- heatmap_df %>% 
  arrange(day_of_week, hour_of_day)

#heatmap_df$day_of_week <- as.character(heatmap_df$day_of_week)
# 
# heatmap_df |>
#   e_charts(day_of_week) |> 
#   e_heatmap(hour_of_day, logins) |> 
#   e_visual_map(logins) |> 
#   e_title(text = "Heatmap of Successful API Requests by Day and Hour",
#           subtext = "24 hour clock") %>% 
#   e_tooltip(trigger = "item") 


# #Trying ggplot
# library(ggplot2)
# library(plotly)
# 
# p <- ggplot(heatmap_df, aes(day_of_week, hour_of_day, fill= logins)) + 
#   geom_tile() + xlab("Day of the Week") + ylab("Hour of the Day") + 
#   ggtitle("Heatmap of Successful API Requests by Day and Hour",
#           subtitle = "24 Hour Clock") +
# scale_fill_gradient(low = "#ece75f",
#                     high = "#610c04",
#                     guide = "colorbar")
# 
# ggplotly(p, tooltip = "all")


#echarts
heatmap_df$day_of_week <- as.character(heatmap_df$day_of_week)

heatmap_df |> 
  distinct(hour_of_day, day_of_week, .keep_all=TRUE) |>
  ec.init(

	title= list(text= "Heatmap of Successful API Requests by Day and Hour"),

	series= list(list(type= 'heatmap')),

	xAxis= list(type= 'category', data= c('Mon','Tue','Wed','Thu','Fri','Sat','Sun')),

	yAxis= list(min= min(heatmap_df$hour_of_day)-1, name= 'hours', interval= 1),

	visualMap= list(calculable= TRUE, max= 100, 

						 orient= 'horizontal', bottom= 'bottom', left='middle', align= 'right', 

						 inRange= list(color= c('yellow','red'))),

	tooltip= list(trigger= "item"))
```


```{r wordcloud, results = 'asis', echo = FALSE}
wordcloud <- as.data.frame(table(df$attributes.params.datasource))

wordcloud |> 
  e_color_range(Freq, color) |> 
  e_charts() |> 
  e_cloud(Var1, Freq, color, shape = "circle") |> 
  e_title("Wordcloud of Data Sources",
          subtext = "Successful Requests Only") %>% 
  e_tooltip(trigger = "item")


#Matching horizontal bar chart
datasource <- df %>% 
  group_by(attributes.params.datasource) %>% 
  summarise(requests = n()) %>% 
  mutate(datasource = "Requests") %>% 
  ungroup()

datasource |>
  group_by(attributes.params.datasource) |>
  e_charts(datasource, reorder = FALSE) |>
  e_bar(requests) |>
  e_title("Successful Requests by Data Source")|>
  e_legend(
      orient = 'horizontal', 
      right = 0, 
      top = 25,
      scroll = TRUE
    ) %>% 
    e_grid(left = 75, top = 120)%>% 
  e_tooltip(trigger = "item") %>% 
  e_flip_coords()


```

```{r piecharts, results = 'asis', echo = FALSE}
get_only <- df %>% 
  filter(attributes.transaction.status_code == 200)

get_only$attributes.params.csv <- ifelse(is.na(get_only$attributes.params.csv), "false", get_only$attributes.params.csv)

csv_table <- as.data.frame(table(get_only$attributes.params.csv, useNA = "ifany"))

csv_table <- csv_table %>% 
  mutate(percent = Freq / sum(Freq)) %>% 
  mutate(type = case_when(
  Var1 == "true" ~ "CSV",
  Var1 == "false" ~ "JSON"
))

csv_table |>
  e_charts(type) |> 
  e_pie(percent, radius = c("50%", "70%")) |> 
  e_title("Proportion of CSV to JSON format") |>
  e_legend(
      orient = 'vertical', 
      right = 0, 
      top = 0,
      scroll = TRUE
    )

```

```{r boxplots, results = 'asis', echo = FALSE}

js_to_hms <- htmlwidgets::JS('function (value) {
  var d = new Number(value);
  var h = Math.floor(d/3600);
  var m = Math.floor(d % 3600 / 60);
  var s = Math.floor(d % 3600 % 60);
  

  
  var hDisplay = h > 0 ? h + (":") : "00:";
  var mDisplay = m > 0 ? m + (":") : "00:";
  var sDisplay = s > 0 ? s : "00";
  
  return hDisplay + mDisplay + sDisplay; 
}')

#boxplot of time to transmit by app

df %>% 

  group_by(attributes.params.datasource) |>
  e_charts() |>
  e_boxplot(time_to_transmit_in_secs, outliers = TRUE
        ) %>% 
  e_title("Time to Transmit by Data Source") %>% 
  e_y_axis(
   time_to_transmit_in_secs, 
     axisLabel = list(
       formatter = js_to_hms
     ),
   margin = 12
    )%>% 
  e_tooltip(trigger = "item") |>
  e_flip_coords()


#Boxplot of time to transmit by method

df |>
  group_by(method) |>
  e_charts() |>
  e_boxplot(time_to_transmit_in_secs, outliers = TRUE
        ) %>% 
  e_title("Time to Transmit by Method",
          subtext = "Successful Requests Only") %>% 
  e_y_axis(
   time_to_transmit_in_secs, 
     axisLabel = list(
       formatter = js_to_hms
     ),
   margin = 12
    )%>% 
  e_tooltip(trigger = "item")

#Boxplot of number of requests per user

requests_per_user <- df %>% 
  group_by(user_id) %>% 
  summarise(requests = n()) %>% 
  ungroup() %>% 
  select(requests)


# requests_per_user |>
#   e_charts(width = 500) |>
#   e_boxplot(requests, outliers = TRUE) %>% 
#   e_title("Successful Requests Per User") %>% 
#   e_tooltip(trigger = "item") %>% 
#   e_x_axis(show = FALSE)# %>% 
#   #e_flip_coords()
  
#Minimum
min.rt <- min(requests_per_user$requests, na.rm = TRUE)

# Lower  Hinge:
RT <- sort(requests_per_user$requests)
lower.rt <- RT[1:round(length(RT)/2)] 
lower.h.rt <- median(lower.rt)

# Median
median.rt <- median(requests_per_user$requests, na.rm = TRUE)

# Upper Hinge
RT <- sort(requests_per_user$requests)
upper.rt <- RT[round((length(RT)/2)+1):length(RT)] 
upper.h.rt <- median(upper.rt)

# Max
max.rt <- max(requests_per_user$requests, na.rm = TRUE)

fivenumber <- cbind(min.rt, lower.h.rt,
                    median.rt, upper.h.rt,
                    max.rt)
colnames(fivenumber) <- c("Min", "25th Percentile",
                       "Median", "75th Percentile", "Max")

formattable(as.data.frame(fivenumber), 
            align = c(rep("c", NCOL(fivenumber))), 
            caption = "Successful Requests Per User")
```


```{r barcharts, results = 'asis', echo = FALSE}
request_by_week <- df %>% 
  group_by(day_of_week) %>% 
  count(method, day_of_week) %>% 
  ungroup()

request_by_week$day_of_week <- as.character(request_by_week$day_of_week)

request_by_week |>
  group_by(method) |>
  e_charts(day_of_week) |>
  e_bar(n) |>
  e_title("Successful Request Type by Day of Week")|>
  e_legend(
      orient = 'vertical', 
      right = 0, 
      top = 0,
      scroll = TRUE
    ) %>% 
    e_grid(left = 50, top = 75)%>% 
  e_tooltip(trigger = "item")


#Barchart of request for each user
requests_by_user <- df %>% 
  group_by(user_id) %>% 
  summarise(requests = n()) %>% 
  ungroup() %>% 
  mutate(userid = "Requests")

requests_by_user |>
 # group_by(user_id) |>
  e_charts(user_id) |>
  e_bar(requests) |>
  e_title("Successful Requests by User")|>
  e_legend(
      orient = 'vertical', 
      right = 0, 
      top = 0,
      scroll = TRUE
    ) %>% 
    e_grid(left = 100, top = 75)%>% 
  e_tooltip(trigger = "item") %>% 
  e_flip_coords()
```


```{r timeseries, results = 'asis', echo = FALSE}

# if (params$timeseries == "day") {
#   df$timeseries <- lubridate::date(df$attributes.transaction.start_datetime)
# }
# 
# if (params$timeseries == "hour"){
#   df$timeseries <- lubridate::hour(df$attributes.transaction.start_datetime)
#   df$timeseries <- as_datetime(paste0(df$start_date, " ", df$timeseries, ":00:00"))
# }

df_raw$start_date <- lubridate::date(df_raw$attributes.transaction.start_datetime)

timeseries <- df_raw  %>% 
  group_by(start_date) %>% 
  summarise(requests = n()) %>% 
  ungroup()

timeseries |>
  e_charts(x = start_date) %>% 
  e_datazoom(
    type = "slider", 
    toolbox = FALSE,
    bottom = -5
  ) %>% 
  e_title("Time Series of Raw Requests",
          subtext = "By Day") %>% 
  e_x_axis(start_date, axisPointer = list(show = TRUE)) %>% 
  e_bar(requests)%>% 
  e_tooltip(trigger = "item")


df_raw$start_hour <- lubridate::hour(df_raw$attributes.transaction.start_datetime)
df_raw$start_hour <- as_datetime(paste0(df_raw$start_date, " ", df_raw$start_hour, ":00:00"))
  
timeseries <- df_raw  %>% 
  group_by(start_hour) %>% 
  summarise(requests = n()) %>% 
  ungroup()


  timeseries |>
  e_charts(x = start_hour) %>% 
  e_datazoom(
    type = "slider", 
    toolbox = FALSE,
    bottom = -5
  ) %>% 
  e_title("Time Series of Raw Requests",
          subtext = "By Hour") %>% 
  e_x_axis(start_hour, axisPointer = list(show = TRUE)) %>% 
  e_bar(requests)%>% 
  e_tooltip(trigger = "item")
```


